Digitization of the Australian Parliamentary Debates, 1998-2022

### 2023-07-06 paper/paper-nature-revised.qmd
Add the aspects I had to redo

The official written record of parliamentary debates, formally known as Hansard, plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions. Originating in the British parliament, the production of Hansard became tradition in many other Commonwealth countries, such as Canada and Australia [@vice2017history]. Given the content and magnitude of these records, they have significance, particularly in the context of political science research. In the case of Canada, the Hansard has been digitized for 1901 to 2019 [@lipad]. Having a digitized version of Hansard enables researchers to conduct text analysis and statistical modelling. Following the lead of that project, in this paper we introduce a similar database for Australia. This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to 2022, containing details on everything said in parliament in a form that can be readily used by researchers. With the development of tools for large-scale text analysis, this database will serve as a resource for understanding political behaviour in Australia over time.

@@

At present, the Hansard format that is available on the Parliament of Australia website is not accessible for large scale analysis. To this point, various researchers have had to create their own databases of usable, complete data based on content from the Australian Parliament website. For instance, @sherratt created an online, easy to read database of Hansard from 1901 to 1980 using the XML files. These data can be navigated by year, parliament, people, and bills [@sherratt]. To make the Australian Parliamentary Handbook more accessible, @Leslie_2021_HoR_Aus has released an `R` package which includes data on all MPs from 1945 to 2019. Further, @auspol created the `AustralianPoliticians` `R` package, which contains several datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021.

Many papers exist which use components of Australian Hansard to explore various research topics. For example, @salisbury2011 used the Hansard to investigate occurrences of unparliamentary comments by MPs, where the Speaker tells that MP to withdraw their remark. @rasiah2010framework worked with Question Time data from Hansard transcripts during February and March of 2003, to investigate resistance of politicians in answering questions about Iraq. @fraussen2018 use Hansard to quantify political prominence by investigating strategic mentions of interest groups by elected officials. Finally, @alexander2021 construct a dataset of the Australian Hansard, along with an analysis of the effect of elections and changes in Prime Ministers upon topics mentioned in parliament. @alexander2021 created this database with the static PDF versions of Hansard, using OCR to digitize these files into text which is suitable for analysis. This means there are considerable digitization errors especially in the first half of the dataset.

@@

>          <hansard>
>            1. <session.header>
>            2. <chamber.xscript>
>               a)  <business.start>
>               b)  <debate>
>                   i.  <debateinfo>
>                   ii. <debate.text>
>                   iii. <speech>
>                   iv. <subdebate.1>
>                       (1) <subdebateinfo>
>                       (2) <subdebate.text>
>                       (3) <speech>
>                       (4) <subdebate.2>
>                           (a) <subdebateinfo>
>                           (b) <subdebate.text>
>                           (c) <speech>
>           3. <fedchamb.xscript>
>           4. <answers.to.questions>
>               a)  <question>
>               b)  <answer>

@@

**Another fundamental component of parliamentary proceedings is voting. In the House, when a question arises such as “The question is that the amendment be agreed to”, Members are asked to cast their vote either in the affirmative or in the negative, and the majority of votes as judged by the Speaker determines the outcome [@australia2018house]. Further, Members can vote in an unofficial arrangement called pairs, in which as written in Chapter 8 of @australia2018house, "can be used to enable a Member on one side of the House to be absent for any votes when a Member from the other side is to be absent at the same time or when, by agreement, a Member abstains from voting". If the result as determined by the Speaker is challenged by more than one MP, this leads to a division of the House in which the question is re-stated and Members must move to the left or right of their chair depending on how they vote, so that the votes can be re-counted and recorded [@australia2018house].**

@@

Our database is available in both CSV and parquet formats. It covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022 **where an XML transcript is available**, so there are **1,532 individual sitting day** files for each format. **Additionally, there is a single corpus file in both CSV and Parquet forms containing the data from all sitting days, with a date variable added to allow for distinction and filtering of individual sitting days. There is also a CSV and Parquet file containing all parsed debate topics.** All data records are available on the general-purpose repository Zenodo, at https://doi.org/10.5281/zenodo.7799678 [@katz_2023]. For each **Hansard data** file, **that is, the corpus and the individual sitting day files**, each row contains an individual statement, with details on the individual speaking. For general statements transcribed as made by "Honourable members" for example, these variables cannot be specified. @tbl-vars provides an overview of each variable found in the **Hansard data files in the** database.

@@

![Number of speeches made on each sitting day in the House of Representatives](n_daily_speeches.png){#fig-dailyspeeches width="440"}

@@

![Daily number of unique names detected in our Hansard data](n_unique_names.png){#fig-names width="440"}

@@

The code written to build this database is available on the GitHub repository associated with this paper: https://github.com/lindsaykatz/hansard-proj. All scripts were created using R software [@r_software]. The core packages used to develop these scripts are: the `XML` package by @XML_pkg, the `xml2` package by @xml2_pkg, the `tidyverse` R packages by @tidyverse, the `AustralianPoliticians` package by @auspol, and the `ausPH` package by @Leslie_2021_HoR_Aus. `XML` and `xml2` were used for parsing the XML documents, `AustralianPoliticians` and `ausPH` were used for cleaning up and filling in MP details in the datasets, and `tidyverse` packages were used in all steps, for tidy wrangling of data.

@@

We thank Kristine Villaluna, Monica Alexander, and Jack Stephenson for helpful comments.

>>>>

The official written record of parliamentary debates, **formally known as Hansard [@citehansard],** plays a fundamental role in capturing the history of political proceedings and facilitating the exploration of valuable research questions. Originating in the British parliament, the production of Hansard became tradition in many other Commonwealth countries, such as Canada and Australia [@vice2017history]. Given the content and magnitude of these records, they have significance, particularly in the context of political science research. In the case of Canada, the Hansard has been digitized for 1901 to 2019 [@lipad]. Having a digitized version of Hansard enables researchers to conduct text analysis and statistical modelling. Following the lead of that project, in this paper we introduce a similar database for Australia. This is composed of individual datasets for each sitting day in the House of Representatives from 1998 to 2022, containing details on everything said in parliament in a form that can be readily used by researchers. With the development of tools for large-scale text analysis, this database will serve as a resource for understanding political behaviour in Australia over time.

**There are a wide variety of potential applications of this database. For instance, within Australia there is considerable concern that there has been a decline in the 'quality' of public policy debate (however that might be defined). Our dataset could be used to look at whether it is really getting worse in particular ways, and if so, why. We might also be interested in whether particular sub-populations are appropriately represented in what is talked about in parliament. For instance, there is often concern that regional areas are overlooked compared with metropolitan areas. Again, our database could be used to examine whether this has changed over time. We have developed our database in such a way that it could be linked with similar databases from other countries which would enable comparative analysis. For instance, we may be interested in how the policy focus of a parliament changes given various global events such as pandemics or wars. An international linkage provides a comparison case where domestic issues are different while international ones are common. As an example of enabling this linkage this we have included partyfacts IDs in our database. This should make it possible to link our database with other large parliamentary speech collection projects, such as ParlaMint [@Erjavec2022], ParlSpeech [@Rauh], ParlEE [@parlee], and MAPLE [@maple].**

@@

At present, the Hansard format that is available on the Parliament of Australia website is not easily accessible for large scale analysis. To this point, various researchers have had to create their own databases of usable, complete data based on content from the Australian Parliament website. For instance, an online, easy to read database of Hansard from 1901 to 1980 using the XML files has been created [@sherratt]. These data can be navigated by year, parliament, people, and bills [@sherratt]. To make the Australian Parliamentary Handbook more accessible, an `R` package which includes data on all MPs from 1945 to 2019 has been created @Leslie_2021_HoR_Aus. Further, there is the `AustralianPoliticians` `R` package, which contains several datasets related to the political and biographical information of Australian federal politicians who were active between 1901 and 2021 @auspol. **And finally, there has been examination of speech and MP level data between 1990 and 2019 in Australia @Dowding2021. Like us they scrape the Hansard record and link it with biographical data. They key difference is that our focus is on the database itself, while  are focused on using a database constructed from the same source to answer a particular question about speaker time. This different focus leads to different emphasis and approaches.**

Many papers exist which use components of Australian Hansard to explore various research topics. For example, the Hansard has been used to investigate occurrences of unparliamentary comments by MPs, where the Speaker tells that MP to withdraw their remark @salisbury2011. Question Time data from Hansard transcripts during February and March of 2003 has been used to investigate resistance of politicians in answering questions about Iraq @rasiah2010framework. Hansard has been used to quantify political prominence by investigating strategic mentions of interest groups by elected officials @fraussen2018. Finally, a dataset of the Australian Hansard has been constructed and then used to analyze the effect of elections and changes in Prime Ministers upon topics mentioned in parliament @alexander2021. This was created with the static PDF versions of Hansard, using OCR to digitize these files into text which is suitable for analysis. This means there are considerable digitization errors especially in the first half of the dataset.

@@

> ```         
>      <hansard>
>        1. <session.header>
>        2. <chamber.xscript>
>           a)  <business.start>
>           b)  <debate>
>               i.  <debateinfo>
>               ii. <debate.text>
>               iii. <speech>
>               iv. <subdebate.1>
>                   (1) <subdebateinfo>
>                   (2) <subdebate.text>
>                   (3) <speech>
>                   (4) <subdebate.2>
>                       (a) <subdebateinfo>
>                       (b) <subdebate.text>
>                       (c) <speech>
>       3. <fedchamb.xscript>
>       4. <answers.to.questions>
>           a)  <question>
>           b)  <answer>
> ```

@@

**Another fundamental component of parliamentary proceedings is voting. In the House, when a question arises such as "The question is that the amendment be agreed to", Members are asked to cast their vote either in the affirmative or in the negative, and the majority of votes as judged by the Speaker determines the outcome [@australia2018house]. Further, Members can vote in an unofficial arrangement called pairs, which "can be used to enable a Member on one side of the House to be absent for any votes when a Member from the other side is to be absent at the same time or when, by agreement, a Member abstains from voting" @australia2018house. If the result as determined by the Speaker is challenged by more than one MP, this leads to a division of the House in which the question is re-stated and Members must move to the left or right of their chair depending on how they vote, so that the votes can be re-counted and recorded [@australia2018house].**

@@

Our database is available in both CSV and parquet formats. Both CSV and parquet are open standards. We provide both because while CSVs are commonly used and can be manually inspected, parquet files are typically smaller and preserve class. Our database covers all sitting days of the House of Representatives from 02 March 1998 to 08 September 2022 **where an XML transcript is available**, so there are **1,532 individual sitting day** files for each format. **Additionally, there is a single corpus file in both CSV and Parquet forms containing the data from all sitting days, with a date variable added to allow for distinction and filtering of individual sitting days. There is also a CSV and Parquet file containing all parsed debate topics.** All data records are available on the general-purpose repository Zenodo, at https://doi.org/10.5281/zenodo.7799678 [@katz_2023]. For each **Hansard data** file, **that is, the corpus and the individual sitting day files**, each row contains an individual statement, with details on the individual speaking. For general statements transcribed as made by "Honourable members" for example, these variables cannot be specified. @tbl-vars provides an overview of each variable found in the **Hansard data files in the** database.

@@

![Number of speeches made on each sitting day in the House of Representatives](images/n_daily_speeches.png){#fig-dailyspeeches width="440"}

@@

![Daily number of unique names detected in our Hansard data](images/n_unique_names.png){#fig-names width="440"}

@@

The code written to build this database is available on the GitHub repository associated with this paper: https://github.com/lindsaykatz/hansard-proj. All scripts were created using R software [@r_software]. The core packages used to develop these scripts are: the `XML` package @XML_pkg, the `xml2` package @xml2_pkg, the `tidyverse` R packages @tidyverse, the `AustralianPoliticians` package @auspol, and the `ausPH` package @Leslie_2021_HoR_Aus. `XML` and `xml2` were used for parsing the XML documents, `AustralianPoliticians` and `ausPH` were used for cleaning up and filling in MP details in the datasets, and `tidyverse` packages were used in all steps, for tidy wrangling of data.

@@

We thank Kristine Villaluna, Monica Alexander, and Jack Stephenson for helpful comments. We wish to especially thank Guy Jones, Chief Editor, the two anonymous reviewers, and the Editorial Board Member, Michael Jankowski for their comments.
